Reanalysis Step 5: Main Effects Outcome Analysis

### 2025-08-31 reanalysis-5-outcome_analysis.qmd
fix coefficient

```{r marginal-effects}
# Check if AMEs are cached
ame_cache_file <- file.path(reanalysis_data_dir, "ame_results_main_effects.rds")
force_recalc_ame <- FALSE  # Set to TRUE to force recalculation

@@

  # Display predictions
  kable(pred_df |> select(Lapse_Status, Predicted_Prob, SE, lower.CL, upper.CL), 
        caption = "Predicted probability of VI/blindness by lapse status (marginalized over all covariates)",
        col.names = c("Lapse Status", "Predicted Probability", "SE", "Lower CI", "Upper CI"),
        digits = 3)

>>>>

```{r marginal-effects}
# Check if AMEs are cached
ame_cache_file <- file.path(reanalysis_data_dir, "ame_results_main_effects.rds")
force_recalc_ame <- TRUE  # Set to TRUE to force recalculation

@@

  # Display predictions
  kable(pred_df |> select(Lapse_Status, Predicted_Prob, SE, asymp.LCL, asymp.UCL), 
        caption = "Predicted probability of VI/blindness by lapse status (marginalized over all covariates)",
        col.names = c("Lapse Status", "Predicted Probability", "SE", "Lower CI", "Upper CI"),
        digits = 3)
